---
title: "Leading Causes of Death in China"
author: "Ning Ning Liu"
date: "Jan 9th 2017"
output:
  ioslides_presentation
---
## Total Population
1.Total population :1.4billion
2.18% of them is under 15 
3.14% of them is over 60
```{r, echo=FALSE, message=FALSE}
library(plotly)
plot_ly(
  type = 'scattergeo',
  lon=c(116.363625),
  lat=c(39.913818),
  text=('China'),
  mode='markers')
```

## Leading Causes of Death in China
1 - Malignant Neoplasms
2 - Heart Disease
3 - Cerebrovascular Disease
4 - Diseases of the Respiratory System
5 - Endocrine, Nutritional&Metabolic Diseases
```{r, echo=FALSE, message=FALSE}
plot_ly(x = c(1,2,3,4,5),
        y=c(0.28,0.21,0.11,0.05,0.034),
        type='bar')
```

## Prediction
Let's say if the data increases 0.1 in the next year 
```{r, echo=FALSE, message=FALSE}
library(plotly)
plot_ly(x = c(1,2,3,4,5),
        y=c(0.38,0.31,0.21,0.15,0.134),
        type='scatter',
        mode='markers')
plot_ly(x = c(1,2,3,4,5),
        y=c(0.28,0.21,0.11,0.05,0.034),
        type='scatter',
        mode='markers')
```

## Recommendation for Business
1 - Malignant Neoplasms
2 - Heart Disease
3 - Cerebrovascular Disease
4 - Diseases of the Respiratory System
5 - Endocrine, Nutritional&Metabolic Diseases
